Discovery of s-process enhanced stars in the LAMOST survey

### 2018-09-08 article/ms.tex
paper progress

\subsection{Observations and data reduction}
On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile. Candidates were observed as part of another program not a detailed follow-up campaign. They were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$. Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon. We reduced the data using the \texttt{CarPy} package \citep{kelson2000}. We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-spaced wavelength map. We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.

\subsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citet{ho2017}. Following the procedure outlined in \citet{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements. The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.

@@

\subsection{Extrinsic or intrinsic}
Barium enhanced stars exist as either intrinsic or extrinsic stellar objects. Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB. This highlights that our sample does not contain stars to the degree of evolution required to reach the TP-AGB phase, and therefore, must be extrinsic barium stars. However, stars with temperatures below 3800K in Figure \ref{fig:figure2} are potential AGB stars, and their intrinsic or extrinsic nature is not certain. Additionally, it's important to note, previous literature \citep{van2017}, state only 33\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars). In comparison, we find that all our barium candidates to be extrinsic. This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous AGB S stars. Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars. Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is exclusively populated by red giant extrinsic barium stars. This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{hrd_new.pdf}
    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.}
    %Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event. The classification of stars with $\log{g} < 2$ would require additional data.}
    \label{fig:figure2}
\end{figure}

\subsection{Sodium enhancement}
Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface of these giants via mixing during the first dredge-up, and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity. Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement. We also note that the 5 sodium-enhanced barium stars all have values of, $\log{g} \approx 3$, which is inconsistent with the literature. Previous studies suggest, lower $\log{g}$ values are expected, given low $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios. It is important to note, sodium enhancement can occur due to the presence of interstellar dust. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption. However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating, the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 barium candidates, but more importantly, sodium enhancement is by no means ubiquitous in barium stars. However, it should be highlighted that low resolution spectra can result in Na line saturation, limiting the flux enhancement even with an abundance enhancement.

The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on barium stars. This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample, and we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars. Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 187 barium star candidate sample. The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts. In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and in accordance with previous literature, it can be concluded that our barium star sample is extrinsic. However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement. Additionally, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.

@@

\subsection{Carbon bands}
Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process. In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star. In an identical mechanism to the presence of s-process element enhancement, carbon enhanced stars exist intrinsically or extrinsically. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 187 barium candidates. These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
%Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.

\subsection{Comparison to AGB yields}
AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement. In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 barium stars identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex). Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$. Given our barium stars exist in this metallicity range of 0 to -1.1, we can classify them as CH stars as defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.

The final surface s-process index [Ba/Sr], illustrated in Figure \ref{fig:figure3}, illustrates the relationship between [Ba/Sr] yields and the mass of AGB stars. This highlights the main neutron source, the $C^{13}(\alpha,n)O^{16}$ reaction chain, is responsible for the Ba and Sr enhancements. Additionally, theoretical models show that this source is dominant in low-mass AGB stars, and it follows, that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$. However, it's important to note, our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses. Instead, mass transfer may have occurred early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may reflect pollution from a lower AGB S star mass. Additionally, this can be extended to our candidates not approximated by theoretical yields. Other barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB S stars within our sample.

%The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.

@@

The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event. Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic distribution of each class of s-process enhanced star investigated. For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk (81\% thin disk and 16\% thick disk), and 3\% within the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo. \cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars. Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources. However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 895 s-process candidates including: 187 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 659 exhibiting exclusively strontium enhancement. This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.  Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars, indicating our barium stars were not produced through an unusual galactic event.

We find 178/257 barium star candidates show carbon enhancement, consistent with the literature, and are possible CH stars. However, in contrast with previous works, we do not find barium stars to have significantly higher [Na/Fe] than Milky Way field giants. Only 5/257 of our barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust. We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.

Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for the Ba and Sr enhancements, the $C^{13}(\alpha,n)O^{16}$ reaction chain, and theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars, between $1 - 3\,M_{\odot}$. We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances. This data would permit the most detailed comparisons with AGB star yields ever considered.

>>>>

\subsection{Observations and data reduction}
On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile. These two candidates were observed as part of another program not a detailed follow-up campaign. They were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$. Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon. We reduced the data using the \texttt{CarPy} package \citep{kelson2000}. We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-spaced wavelength map. We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.

\subsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citet{ho2017}. Following the procedure outlined in \citet{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements. The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.

@@

\subsection{Extrinsic or intrinsic}
S-process enrichment can be explained by intrinsic or extrinsic phenomena. Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Previous literature \citep{van2017} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic). In comparison, Figure \ref{fig:figure2} shows that the majority of our sample have temperatures and luminosity not covered by the AGB. This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates. This is in agreement with our sample selection given we were predominantly restricted to RGB stars. However stars with temperatures below 3800K in Figure \ref{fig:figure2} are consistent with being AGB stars, and their intrinsic or extrinsic nature is not certain.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{hrd_new.pdf}
    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 187 s-process candidates from LAMOST.}
    %Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event. The classification of stars with $\log{g} < 2$ would require additional data.}
    \label{fig:figure2}
\end{figure}

\subsection{Sodium enhancement}
Sodium overabundances observed in the atmospheres of giants are primarily synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface via mixing during the first dredge-up and stars with masses more than $1.5\,M_\odot$ can show enhanced sodium abundances \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported  enhanced sodium in 3 of their 16 barium star candidates. They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values. Similarly, \citet{decastro2016} proposes a possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

%however, these [Na/Fe] ratios do not exhibit variations in metallicity
We find that less than $3$\,\% of our s-process candidates show enhanced sodium all of which have values of $\log{g} \approx 3$. It is possible our 5/187 enhanced sodium candidates are false-positives resulting from interstellar dust absorption. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35 confirming that the flux residuals around the Na doublet are due to interstellar absorption. However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values indicating the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 s-process candidates. It also highlights sodium enhancement is by no means ubiquitous in s-process candidates. Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
%Previous studies \citep[e.g.,][]{decastro2016} suggest lower $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.

The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on s-process candidates. This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic s-process candidates (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample. We find that s-process candidates do not have higher [Na/Fe] abundance ratios on average.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic s-process candidates. Our analysis searches for flux residuals around the Tc enhancement lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. We found 51/187 of our s-process candidates to show enhanced Tc at the single line 4238,\AA. The majority (46/51) have $\log{g} > 2$ suggesting they cannot be AGB S stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However we caution that Tc enhancement is usually a very weak signature and would require multiple lines of enhancement. Since all 51 matches were at single lines we concluded Tc enhanced candidates are more likely a result of data artefacts. Also, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}. We therefore conclude our analysis finds no enhanced Tc s-process candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}. The absence of Tc indicates our s-process candidates are not massive enough to produce the element, and suggests that our sample is populated solely by extrinsic s-process candidates.

@@

\subsection{Carbon bands}
During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions at lines 4050\,\AA\hspace{0.5mm} and 4550\,\AA. We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$). These 178 stars have in a metallicities ranging of 0 to -1.2, and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}, we simply define them as metal poor s-process candidates.

\subsection{Comparison to AGB yields}
In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 s-process candidates identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex). The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process pollution and is an indication of the binary AGB companion's mass. The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}. This suggests that the main neutron source for s-process enhancement in our sample is the $C^{13}(\alpha,n)O^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$. However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses. Mass transfer may have occurred early on in the AGB S binary companion star's lifespan. The resulting [Ba/Sr] abundance present in our s-process candidates and those not approximated by theoretical curves may reflect pollution from a lower AGB S star mass. Our s-process candidates that deviate from this relationship may also represent the possibly more massive and exceptionally rarer AGB S stars within our sample.

@@

The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk. Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position of each class of s-process enhanced star investigated. For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk  and 3\% with velocity consistent to the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk and 25\% within the halo. \cite{pereira2011}’s entire sample resides within the disk. Although, these studies contain limited populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars. \cite{decastro2016} contains a more extensive sample and has similar trends to our findings with a 90\% thin disk membership. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, concluding intrinsic s-process candidates are more concentrated towards the galactic plane. Since our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources. However given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars. Or this may be the result of our sample being bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars.

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 895 s-process enhanced stars including; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment. This sample size is the greatest total number of s-process candidates known, and represents the largest sample of s-process enhanced stars to date.  We found our sample contains 97\% disk star membership and 3\% with velocity consistent to the halo.

We find the majority (178/257) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars. However contrary to previous works we do not find our s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants. Only 5/257 of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust. We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.

Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for s-process enhancement is the $C^{13}(\alpha,n)O^{16}$ reaction chain. Theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars between $1 - 3\,M_{\odot}$. We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances and perform a comprehensive comparison of AGB star models.
